---
title             : "Relations between Inflammation, access to care and Diabetes in two repesentative populations of China and Mexico."
shorttitle        : "Inflammation, access to care and Diabetes in China and Mexico."

author: 
  - name          : "Dominik Grätz"
    affiliation   : "1"
    email         : "dgrtz@uoregon.edu"
  - name          : "Rachel Miller-Moudgil"
    affiliation   : "1"
    email         : "rmillerm@uoregon.edu"
  - name          : "Amber Somarriba"
    affiliation   : "1"
    email         : "asomarri@uoregon.edu"
  - name          : "Brittany Spinner"
    affiliation   : "1"
    email         : "bspinner@uoregon.edu"
  - name          : "Tian Walker"
    affiliation   : "1"
    email         : "twalker@uoregon.edu"

affiliation:
  - id            : "1"
    institution   : "University of Oregon"
    
authornote: "List of group members ordered by alphabet."

abstract: "*Background.* Background goes here. *Methods.* Methods go here. *Results.* Results here. *Conclusions.* Conclusions here."

keywords          : "Diabetes, access to care, inflammation, health, Mexico, China"
wordcount         : "X (this cannot easily be done automatically, we can also just leave it out)"

bibliography      : ["../r-references.bib"]

floatsintext      : yes
figurelist        : yes
tablelist         : yes
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = FALSE, echo = FALSE, warning = FALSE, results = FALSE)
library(tidyverse)
library(rio)
library(here)
library(papaja)
```

```{r}
#code used to create extracted data file - China 
#china_survey <- import("China_IND.sav") 
#china_bio <- import( "ChinaLABData.csv", setclass = "tbl_df")
#china_survey$id <- as.numeric(china_survey$id)
#china <- china_survey %>%
#left_join(china_bio, by = 'id')

#china_raw_dat <- china |>
#select(income, q4022,  sex = q0406 , q0407, hba1c, crp, q4023a, q4024, weight = q2507, height = q2506, waist = q2508, marriage = q0408, q2000:q2024 ) |>
#rename(diagnosis = q4022, age = q0407, medication = q4023a, dt_exrcse = q4024 )

#write_csv(china_raw_dat, file = "china_raw_dat.csv")
```

```{r}
#code used to create extracted data file - Mexico 

#mex_survey <- import("Mexico_IND.sav")

#mex_bio <- import("MexicoLabData.csv")

#mex_survey$id <- as.numeric(mex_survey$id)
#mexico <- mex_survey %>%
#left_join(mex_bio, by = 'id')

#mexico_raw_dat <- mexico %>% 
# select(income, q4022,  sex = q0406 , q0407, hba1c, crp, q4023a, q4024, weight = q2507, height = q2506, waist = q2508, marriage = q0408, q2000:q2024 ) |>
#rename(diagnosis = q4022, age = q0407, medication = q4023a, dt_exrcse = q4024 )

#write_csv(mexico_raw_dat, file = "mexico_raw_dat.csv")

```


```{r}
library(here)
library(tidyverse)
library(rio)
library(gridExtra)
```

# Introduction

Enter text/code here. I make a reference here [@example_ref].
**This is just copied from the outline document; needs to be rewritten/references automated!**

## About the data:
We will be using two datasets from the Wave 1 Study on Global Ageing (SAGE) from the World Health Organization (WHO). We will be looking at inflammation (measured through C-reactive protein; crp) and hemoglobin A1c (average blood glucose level over the last three months) to better understand the relationship between inflammation and diabetes in Mexico and China. Observations of the potential association between diabetes and inflammation were initially made over 100 years ago (Williamson, 1901), and we now know that inflammation is a pathogenic mediator in the progression of diabetes, and likely has a causal role in some cases as well (Tsalamandris et al., 2019). The relationship between inflammation and diabetes is multifaceted but we know that decreasing inflammation means decreasing diabetes progression and complications (Agrawal & Kant, 2014).
The data is from two datasets designed exactly the same: one from Mexico and one from China. The data frame for China has 13,367 observations from 1,489 variables. In the dataset from Mexico there are 2,315 observations of 1690 variables. Everything else is the same as the dataset from China. Almost all of the variables are numbers or characters, and the data was originally formatted in SPSS (statistical package for the social sciences). There were more people who did the survey than did the biomarker collection (source of CRP and HbA1c data) so the number of data points in our study is smaller than the full dataset. There is demographic information along with many health-related validated scales. We have listed the variables that we will be looking at below

## Why China and Mexico?

China and Mexico are interesting places to study the relationship between diabetes and inflammation because they are both classified as low to middle income countries (LMIC’s) where 80% of the global burden of diabetes falls. Additionally, diabetes is a leading cause of death in Mexico and closely linked to the obesity epidemic. China experienced a famine that likely created an epigenetic environment that makes people prone to diabetes. Obesity is a relatively new phenomenon in China and so the pathophysiology of disease development may be different than other places where obesity has been a major issue for decades. 


# Methods


# Results

Enter text/code here. Let's do all the coding here!

```{r}
china <- import(here("data","china_raw_dat.csv"))
mexico <- import(here("data","mexico_raw_dat.csv"))
```

```{r Data Cleaning}
#variable creation and cleaning 

#Must filter CRP greater than 5 because such values indicate infection which we don't want

#we also want to filter anyone younger than 50 as they are solely a reference group not used in this analysis

#adding the countries
china <- china %>%
  mutate(country = "China")

mexico <- mexico %>%
  mutate(country = "Mexico")

# table(china$sex)
# table(mexico$sex)


#combining data into one, log transform

#we only want to log transform hba1c in China. It is normally distributed in Mexico. 

#We can't bind the data because the variables all have exactly the same names.
#We can use GridExtra to put graphs side by side, but we don't need to put the data together.
#OR if we put the data together we need to rename all of the variables with a c or m on them. 

data <- bind_rows(china, mexico) %>%
  mutate(hba1c_log = log(hba1c), .after = hba1c) %>%
  filter(age >=50, crp <5)

#creating the sum and mean composite scores for the health variables (p2000:2049 except for 2020: and q2049 as they are not measured on a 1-5 scale).


# q <- c("q2000", "q2001","q2002","q2003","q2004","q2005","q2006","q2007","q2008","q2009","q2010","q2011","q2012","q2013","q2014","q2015","q2016","q2017","q2018","q2019","q2023","q2024","q2025","q2026","q2027","q2028","q2029","q2030","q2031","q2032","q2033","q2034","q2035","q2036","q2037","q2038","q2039","q2040","q2041","q2042","q2043","q2044","q2045","q2046","q2047","q2048") #list of relevant health variables

#table(data$country)
# data <- data %>% 
# group_by(country) %>% 
#   mutate(q_sum = q2000+q2001+q2002+q2003+q2004+q2005+q2006+q2007+q2008+q2009+q2010+q2011+q2012+q2013+q2014+q2015+q2016+q2017+q2018+q2019+q2023+q2024+q2025+q2026+q2027+q2028+q2029+q2030+q2031+q2032+q2033+q2034+q2035+q2036+q2037+q2038+q2039+q2040+q2041+q2042+q2043+q2044+q2045+q2046+q2047+q2048, na.rm=TRUE, .after=q2049) %>% mutate(q_mean = q_sum/33, .after=q_sum) #This code returns an error, but not sure where the issue is. Tried using mutate(q_sum = q) but it did not like that either!

#View(data)

#simplified health questionnaire code
qnumbers <- c(2000:2019, 2023:2048)
q <- paste0("q", qnumbers)

data <- data %>%
  mutate(across(q, ~ifelse(.x > 5, NA, .x))) %>% #this will get rid of responses over 5 which indicate missing or NA
  rowwise() %>%
  mutate(q_mean = mean(c_across(q), na.rm = TRUE), .after = q2049)

#dichotomized variable for blood sugar that is in range or not
#diabetes variable that includes people who are undiagnosed (i.e. hba1c above 6.5 but no diabetes diagnosis)

data <- data %>% 
  mutate(a1c_dichot_words = ifelse(hba1c>= 6.5, "elevated", "in-range" )) %>%
  filter(!is.na(diagnosis)) %>%
  mutate(diabetes=if_else(diagnosis==1|hba1c>6.5,1,0)) 

#variable that indicates whether someone was doing both medication and diet/exercise intervention

data <- data %>%
  mutate(both_trtmnt = ifelse( medication ==1|dt_exrcse==1, 1, 0))

```

```{r Descriptives Table}
#get descriptives

summary <- data %>%
  group_by(country) %>%
  summarize(N = n(),
            N_male = sum(sex == 1, na.rm = TRUE), #1 is male
            N_male_pct = round((N_male/N*100), 1),
            N_female = sum(sex == 2, na.rm = TRUE),
            N_female_pct = round((N_female/N)*100, 1),
            N_unknown = sum(is.na(sex)),
            N_unknown_pct = round((N_unknown/N)*100, 1),
            diabetes_diag = sum(diagnosis == 1, na.rm = TRUE),
            diabetes_diag_pct = round((diabetes_diag/N)*100, 1),
            diabetes_undiag = sum(hba1c >= 6.5 & diagnosis == 2, na.rm = TRUE),
            diabetes_undiag_pct = round((diabetes_undiag/N)*100, 1),
            age_M = round(mean(age), 1),
            age_SD = round(sd(age), 1))
```


```{r Reg1_HBA1C-CRP}

#Regression 1: only diabetes population: hba1c regressed onto CRP among those doing medication or not

data$medication <- as.factor(data$medication )

data_dia <- data %>% 
  filter(diagnosis == 1)

mreg1 <- lm(crp~hba1c + medication, data = data_dia[data_dia$country=="China",])

mreg1_plot <- data %>% 
  filter(diagnosis == 1) %>% 
  ggplot(aes(hba1c, crp)) +           
  geom_point(aes(color = medication)) +  
  geom_smooth(method = "lm", aes(color = medication)) 
#+facet_wrap(~country)
  
# This doesn't seem to be creating a line
  #stat_smooth(method = "lm",
             # formula = mreg1,
              #geom = "smooth")

summary(mreg1)

creg1 <- lm(crp~hba1c + medication, data =data[data$country=="Mexico",])

creg1_plot <- data %>% 
  filter(diagnosis == 1) %>% 
  ggplot(aes(hba1c, crp)) +           
  geom_point(aes(color = medication)) +                    
  stat_smooth(method = "lm",
              formula = creg1,
              geom = "smooth") 

grid.arrange(creg1_plot, mreg1_plot)

```

```{r echo=FALSE}
mreg1_plot
```

```{r}
#need to duplicate in China
mreg1 <- lm(crp~hba1c, data = mexico)
mreg1_plot <- ggplot(mexico, aes(hba1c, crp)) +           
  geom_point() +                                     
  stat_smooth(method = "lm",
              formula = mreg1,
              geom = "smooth") +
  facet_wrap(~both_trtmnt)
summary(mreg1)

creg1 <- lm(crp~hba1c, data = china)
creg1_plot <- ggplot(china, aes(hba1c, crp)) +           
  geom_point() +                                     
  stat_smooth(method = "lm",
              formula = creg1,
              geom = "smooth") +
  facet_wrap(~both_trtmnt)
summary(creg1)

```


```{r Reg2_HBA1C-CRP}

#Regression 2: same as above adding health state description into model
#Hypothesis: people who opt to talk to a doctor and seek intervention are the least healthy 

reg2 <- lm(crp~hba1c + q_mean, data = data)
reg2_plot <- ggplot(data, aes(hba1c, crp)) +           
  geom_point() +                                     
  stat_smooth(method = "lm",
              formula = reg2,
              geom = "smooth") +
  facet_wrap(~both_trtmnt)

summary(reg2)
```

```{r}
#We did this above this is unnecessary!
china <- china %>%
  mutate(q_sum = q2000+q2001+q2002+q2003+q2004+q2005+q2006+q2007+q2008+q2009+q2010+q2011+q2012+q2013+q2014+q2015+q2016+q2017+q2018+q2019+q2023+q2024+q2025+q2026+q2027+q2028+q2029+q2030+q2031+q2032+q2033+q2034+q2035+q2036+q2037+q2038+q2039+q2040+q2041+q2042+q2043+q2044+q2045+q2046+q2047+q2048, na.rm=TRUE, .after=q2049) %>% mutate(q_mean = q_sum/33, .after=q_sum)
mexico <- mexico %>%
  mutate(q_sum = q2000+q2001+q2002+q2003+q2004+q2005+q2006+q2007+q2008+q2009+q2010+q2011+q2012+q2013+q2014+q2015+q2016+q2017+q2018+q2019+q2023+q2024+q2025+q2026+q2027+q2028+q2029+q2030+q2031+q2032+q2033+q2034+q2035+q2036+q2037+q2038+q2039+q2040+q2041+q2042+q2043+q2044+q2045+q2046+q2047+q2048, na.rm=TRUE, .after=q2049) %>% mutate(q_mean = q_sum/33, .after=q_sum)
```

```{r}
#need to duplicate in China
creg2 <- lm(crp~hba1c + q_mean, data = china)
creg2_plot <- ggplot(china, aes(hba1c, crp)) +           
  geom_point() +                                     
  stat_smooth(method = "lm",
              formula = reg2,
              geom = "smooth") +
  facet_wrap(~both_trtmnt)
mreg2 <- lm(crp~hba1c + q_mean, data = mexico)
mreg2_plot <- ggplot(mexico, aes(hba1c, crp)) +           
  geom_point() +                                     
  stat_smooth(method = "lm",
              formula = reg2,
              geom = "smooth") +
  facet_wrap(~both_trtmnt)
#from Tian- maybe we should facet_wrap by country and color by treatment? 
#Also both_treatment is yes/no people doing both treatments or not so we should also look at dt_excrse and medication. 

summary(mreg2)
summary(creg2)


```

```{r}
#Tian - I got excited and looked at in the subgroup of people with "healthy" a1c levels

mex_sub <- mexico %>% 
  filter(hba1c < 6.5)
mreg3 <- lm(crp~hba1c + q_mean, data = mex_sub)

summary(mreg3)
mexico %>% 
#filter(diabetes == "yes")
ggplot(aes(crp, q_mean)) +           
  geom_point(aes(color = as.factor(medication))) +          stat_smooth(method = "lm",
              formula = reg2,
              geom = "smooth") 
  #facet_wrap(~dt_exrcse)


#names(mexico)
#table(mexico$diabetes)
#names(mexico)
```


```{r Reg3_add-acccess, eval=FALSE, echo=FALSE}

#Regression 3: adding access to care variable into regression model. This chunk is should remain hidden and not evaluated until we decide whether to analyze access to healthcare.

reg3 <- lm(crp~hba1c + q_mean + access, data = data) #Access = whatever variable we come up with for access to helathcare.
reg3_plot <- ggplot(data, aes(hba1c, crp)) +           
  geom_point() +                                     
  stat_smooth(method = "lm",
              formula = reg3,
              geom = "smooth") +
  facet_wrap(~both_trtmnt)

```

The descriptive statistics for our sample look as follows:

|        |                                   |`r summary$country[1]`                                                |`r summary$country[2]`                                                |
|:-------|:----------------------------------|:---------------------------------------------------------------------|:---------------------------------------------------------------------|
|N       |                                   |`r summary$N[1]`                                                      |`r summary$N[2]`                                                      |
|Sex     |                                   |                                                                      |                                                                      |
|        |male                               |`r summary$N_male[1]` (`r summary$N_male_pct[1]` %)                   |`r summary$N_male_pct[2]` (`r summary$N_male_pct[2]` %)               |
|        |female                             |`r summary$N_female[1]` (`r summary$N_female_pct[1]` %)               |`r summary$N_female_pct[2]` (`r summary$N_female_pct[2]` %)           |
|        |unknown                            |`r summary$N_unknown[1]` (`r summary$N_unknown_pct[1]` %)             |`r summary$N_unknown[2]` (`r summary$N_unknown_pct[2]` %)         |
|Age     |                                   |`r summary$age_M[1]` (SD = `r summary$age_SD[1]`)                     |`r summary$age_M[2]` (SD = `r summary$age_SD[2]`)                     |
|Diabetes|                                   |                                                                      |                                                                      |
|        |diagnosed                          |`r summary$diabetes_diag[1]` (`r summary$diabetes_diag_pct[1]` %)     |`r summary$diabetes_diag[2]` (`r summary$diabetes_diag_pct[2]` %)     |
|        |undiagnosed                        |`r summary$diabetes_undiag[1]` (`r summary$diabetes_undiag_pct[1]` %) |`r summary$diabetes_undiag[2]` (`r summary$diabetes_undiag_pct[2]` %) |

Table: Descriptive statistics.



# Discussion

Enter text/code here.

\newpage

# References


\listoftables
\listoffigures

