---
title             : "Relations between Inflammation, access to care and Diabetes in two repesentative populations of China and Mexico."
shorttitle        : "Inflammation, access to care and Diabetes in China and Mexico."

author: 
  - name          : "Dominik Grätz"
    affiliation   : "1"
    email         : "dgrtz@uoregon.edu"
  - name          : "Rachel Miller-Moudgil"
    affiliation   : "1"
    email         : "rmillerm@uoregon.edu"
  - name          : "Amber Somarriba"
    affiliation   : "1"
    email         : "asomarri@uoregon.edu"
  - name          : "Brittany Spinner"
    affiliation   : "1"
    email         : "bspinner@uoregon.edu"
  - name          : "Tian Walker"
    affiliation   : "1"
    email         : "twalker@uoregon.edu"

affiliation:
  - id            : "1"
    institution   : "University of Oregon"
    
authornote: "List of group members ordered by alphabet."

abstract: "*Background.* Background goes here. *Methods.* Methods go here. *Results.* Results here. *Conclusions.* Conclusions here."

keywords          : "Diabetes, access to care, inflammation, health, Mexico, China"
wordcount         : "X (this cannot easily be done automatically, we can also just leave it out)"

bibliography      : [references.bib]
link-citations    : true

floatsintext      : yes
figurelist        : yes
tablelist         : yes
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = FALSE, warning = FALSE, echo = FALSE)
library(tidyverse)
library(rio)
library(here)
library(papaja)
library(janitor)
library(tidyr)
library(stargazer)
source(file = here("scripts", "report_p.R"))
```

```{r data-cleaning-tian, echo=FALSE, eval=FALSE}
#code used to create extracted data file - Mexico 
#Rachel's note: This does not need re-run, as this was Tian joining two Mexico datasets and renaming variables and outputting mexico_raw_dat.csv. We should leave the code here so Joe can see how much initial data cleaning she worked on.
#great idea #dg

mex_survey <- import("Mexico_IND.sav")

mex_bio <- import("MexicoLabData.csv")

mex_survey$id <- as.numeric(mex_survey$id)
mexico <- mex_survey %>%
  left_join(mex_bio, by = 'id')

mexico_raw_dat <- mexico %>% 
  select(income, q4022,  sex = q0406 , q0407, hba1c, crp, q4023a, q4024, weight = q2507, height = q2506, waist = q2508, marriage = q0408, q2000:q2024) %>% 
  rename(diagnosis = q4022, age = q0407, medication = q4023a, dt_exrcse = q4024)

write_csv(mexico_raw_dat, file = "mexico_raw_dat.csv")
```

```{r data-cleaning-rachel, echo=FALSE}
#Rachel's code to drop irrelevant variables, filter, and add a medication*dt_exrcse variable.

data <- import(here("data","mexico_raw_dat.csv")) %>% as_tibble #Importing the Mexico dataset
data <- data %>% 
  select(sex, diagnosis, age, hba1c, crp, medication, dt_exrcse, q5026) %>% 
  rename(access = q5026) %>% 
  filter(age >=50 & diagnosis == 1 & crp < 5) %>% 
  as_tibble() #Selecting only relevant variables, renaming for clarification, and filtering for people with a diabetes diagnosis and high levels of inflammation (crp).

data <- data %>% 
  mutate(med_dt_exrcse = medication*dt_exrcse, .after=dt_exrcse) %>% 
  mutate(med_dt_exrcse = dplyr::recode(med_dt_exrcse, '4' = "1", '1' = "2", '2' = "2")) #Adding a new column for people who both take medication AND diet and exercise. 1 = yes for both, 2 = not yes for both

#making categorical variables factors
data <- data %>%
  mutate(sex = as.factor(sex),
         diagnosis = as.factor(diagnosis),
         medication = as.factor(medication),
         dt_exrcse = as.factor(dt_exrcse),
         med_dt_exrcse = as.factor(med_dt_exrcse),
         access = as.factor(access))

#For our own sanity, this is a mini dataframe of variable descriptions and their coding criteria (if applicable).
col1 <- c("sex","diagnosis","age","hba1c","crp","medication","dt_exrcse","med_dt_exrcse","access","num_care")
col2 <- c("participant gender as reported by researcher (male = 1, female = 2)","whether the participant has been diagnosed with diabetes (yes = 1, no = 2)","participant age","participant blood sugar level","participant inflammation level","whether the participant is currently taking medication for diabetes inflammation (yes = 1, no = 2)","whether the participant is on a diabetes-specific diet and exercise plan (yes = 1, no = 2)","whether the participant is on BOTH medication and a diet and exercise plan (yes = 1, no = 2)","whether the participant has accessed medical care in the past year (1 = yes, 2 = no)","number of times the participant has accessed medical care in the past year")
data_variables <- data.frame(col1, col2)

```

```{r pivot-group_by, echo=FALSE}
#Code to fulfill all of Joe's requirements.

#pivot_wider, to investigate crp levels by sex
crp_by_sex <- data %>% pivot_wider(names_from="sex", values_from="crp") %>% rename(male="1",female="2") %>% as_tibble

#pivot_longer, to investigate medication by crp level
medication_by_crp <- data %>% pivot_longer(cols = "crp", "medication", values_to = "crp","on medication?", names_repair = "unique") #This isn't really doing what I want it to, but I'm out of time for now. -Rachel

#group_by, to look at the mean crp of participants who both take medicine and diet and exercise, versus those who don't.
groups_med_dt_exrcse <- data %>%
  group_by(medication, dt_exrcse) %>% 
  dplyr::summarize(mean = mean(crp)) %>% 
  as_tibble()
```

```{r RQ1, echo=FALSE, render = 'normal print'}
#RQ1: Does taking medication lower inflammation levels? (Requires filtering, modeling, a table, and a figure. Do only as much as possible in this timeframe!)

RQ1_df <- data %>% 
  filter(!is.na(medication & !is.na(hba1c) & !is.na(age) & is.na(crp))

mreg1 <- lm(crp~age + medication, data = RQ1_df)
summary(mreg1) #No significant findings. Oh well!

#mreg1_plot <- ggplot(RQ1_df, aes(medication, hba1c, age)) + geom_point() + stat_smooth(method = "lm", formula = mreg1, geom = "smooth") #This plot looks terrible right now, so I will see if we need to come back to it later.

```

```{r}
RQ1_df %>% 
  ggplot(aes(hba1c, crp)) + 
  geom_point(aes(color = medication), alpha = 0.5) + 
  geom_smooth(aes(color = medication), method = "lm") + 
  scale_color_brewer(palette = 7) + 
  theme_dark() + 
  labs( title = "The Relationship Between Blood Sugar and Inflammation by Medication", 
        caption =  "SAGE data from Mexico", 
        x = "Blood Sugar (HbA1c)", 
        y = "Inflammation (CRP)")
```


```{r eval=FALSE, error=TRUE, message=TRUE, warning=TRUE, include=FALSE}
mod1_summary<- summary(mod1)
table1 <- apa_print(mod1)
table1$table$predictor <- c('Intercept', 
                            'Hba1c',
                            'Diet_Exercise',
                            'Age',
                            'variable')
apa_table(table1$table,
          caption = "Interaction of HbA1c and Medication on CRP ",
          note = paste("Model fit: $F$(", mod1_summary$fstatistic[2], ", ", mod1_summary$fstatistic[3], ") = ", round(mod1_summary$fstatistic[1], 2), ",", "$p$ ", report_p(get_model_p(mod1_summary)), ", ", "$R^2$ = ", round(mod1_summary$r.squared, 2), sep = ""))
```

\newpage 

```{r RQ2, echo=FALSE, comment = NA}
#RQ2: Does diet and exercise predict inflammation levels? (Requires filtering, modeling, a table, and a figure. Do only as much as possible in this timeframe!)
RQ2_df <- data %>%
  filter(!is.na(dt_exrcse) & !is.na(hba1c) & !is.na(age), !(is.na(crp)))

reg2 <- lm(crp ~ age + dt_exrcse, data = data)
stargazer(reg2, type = "text")

#Could not get the summary table to work! (AS)
reg2_summary <- summary(reg2)
table2 <- apa_print(reg2)
table2$table$predictor <- c('Intercept',
                            'Hba1c',
                            'dt_exrcse2',
                            'age',
                            'hba1c:dt_exrcse2')

```



```{r RQ3-brittany}
#RQ3: For those with vs. without access to medical care, what is the effect of diet and exercise on inflammation levels? (Requires filtering, modeling, a table, and a figure. Do only as much as possible in this timeframe!)

# data <- import(here("data","mexico_raw_dat.csv")) %>% as_tibble #Importing the Mexico dataset #From Rachel: I'm hashtagging this out, because if you re-import the dataset here, it loses all the cleaning from earlier. 
 #filter(!is.na(medication) | !is.na(hba1c) | !is.na(age) | !is.na(crp))
RQ3df <- data %>% 
  filter(!is.na(dt_exrcse) & !is.na(hba1c) & !is.na(age), !(is.na(crp)), !is.na(access)) #From Rachel: There were inconsistencies from the cleaning to here about the variable being called care vs. access. I switched them all to access, here and in the code below.

RQ3df <- RQ3df %>% select(diagnosis, age, crp, dt_exrcse, access) %>%  
  filter(age >=50 & (diagnosis == 1 | crp < 5))

RQ3df$access <- factor(RQ3df$access,
                      levels = c(1,2), labels = c("Yes","No")) 
table(RQ3df$access)
tibble(RQ3df)

RQ3df$crp[RQ3df$crp < 2.5] <- "low"
RQ3df$crp[RQ3df$crp > 2.6] <- "high"

tibble(RQ3df$crp)
RQ3df$crp <- RQ3df %>% mutate(category=cut(crp, 
                                           breaks=c(2.5, 2.6), 
                                           labels=c("low","high")))
min(RQ3)
tibble(RQ3df$crp)

#if_else <3 low, otherwise 

table(RQ3df$crp)

prop <- prop.table(table(RQ3df$access))
prop2 <- prop.table(table(RQ3df$crp))
prop
prop2

RQ3_barplot <- barplot(prop, xlab = "Individuals 50yo or older with Diabetes that partake in Diet&/Exercise and saw a Dr. in the Last Year", ylab = "Proportion of Individuals", main = "L") #need to add title and subtitle(?)

#chi_df <- chisq.test(RQ3df$access, RQ3df$crp) #need to get rid of NA values in care and possible create two dfs with yes no and then run chi between dfs of data$care but this is the code 
#chi_df
#chi_df$expected
#chi_df$observed 

#w/ hba1c
RQ4df <- RQ3df %>% select(diagnosis, age, hba1c, crp, dt_exrcse, access) %>%  filter(age >=50 & (diagnosis == 1 | crp < 5 | hba1c >= 6.5)) 

RQ4df$access <- factor(RQ4df$access,
                      levels = c(1,2), labels = c("Yes","No")) 

RQ4df$crp <- RQ4df %>% 
  mutate(crp2 = factor(ifelse(crp <= 3.0, "low", "high"), levels = c("low", "high")))



```


```{r descriptives table prep}
summary <- data %>%
  summarize(country = "Mexico",
            N = n(),
            N_male = sum(sex == 1, na.rm = TRUE), #1 is male
            N_male_pct = round((N_male/N*100), 1),
            N_female = sum(sex == 2, na.rm = TRUE),
            N_female_pct = round((N_female/N)*100, 1),
            N_unknown = sum(is.na(sex)),
            N_unknown_pct = round((N_unknown/N)*100, 1),
            diabetes_diag = sum(diagnosis == 1, na.rm = TRUE),
            diabetes_diag_pct = round((diabetes_diag/N)*100, 1),
            diabetes_undiag = sum(hba1c >= 6.5 & diagnosis == 2, na.rm = TRUE),
            diabetes_undiag_pct = round((diabetes_undiag/N)*100, 1),
            age_M = round(mean(age), 1),
            age_SD = round(sd(age), 1))
summary
```

```{r table of crp medication + exercise}
ggplot(groups_med_dt_exrcse, aes(medication, mean))+
  geom_col(aes(fill = dt_exrcse),
           position = "dodge")+
  labs(x = "Medication",
       y = "Mean CRP Level",
       title = "Mean CRP levels for medication and exercise groups")+
  scale_fill_discrete(name = "Exercise", labels = c("Yes", "No"))+
  scale_x_discrete(labels=c("Medication", "No Medication"))

```


```

The descriptive statistics for our sample look as follows:

\newpage

|  |            |`r summary$country[1]` |
|:-|:-----------|:----------------------|
|$N_{total}$|           |`r summary$N[1]`                                                     |
|Sex        |           |                                                                     |
|           |male       |`r summary$N_male[1]` (`r summary$N_male_pct[1]` %)                  |
|           |female     |`r summary$N_female[1]` (`r summary$N_female_pct[1]` %)              |
|           |unknown    |`r summary$N_unknown[1]` (`r summary$N_unknown_pct[1]` %)            |
|Age        |           |`r summary$age_M[1]` ($SD$ = `r summary$age_SD[1]`)                  |
|Diabetes   |           |                                                                     |
|           |diagnosed  |`r summary$diabetes_diag[1]` (`r summary$diabetes_diag_pct[1]` %)    |
|           |undiagnosed|`r summary$diabetes_undiag[1]` (`r summary$diabetes_undiag_pct[1]` %)|
Table: Descriptive statistics.


# Introduction

Diabetes and its insidious complications continue to expand as a global health burden at an alarming rate. As of 2021, there were approximately 537 million adults living with diabetes in the world and this number is expected to jump to 783 million by 2045. A disproportionate percentage of these people live in low to middle income countries (LMICs). In light of the Covid pandemic, it is also of great import that we better understand the relationships between diabetes and infectious diseases as diabetes both increased the severity of Covid (in people with elevated a1c levels) and has increased in incidence during the Covid 19 pandemic [@yangPrevalenceComorbiditiesIts2020] [@rohmInflammationObesityDiabetes2022].

Additionally, diabetes is associated with a steep increase in cardiovascular disease risk and is a leading cause of death in many low to middle income countries (LMICs) including Mexico. Although the precise classification of diabetes remains controversial because of the complex nature of its pathogenesis, there are three universally acknowledged subtypes: type 1 diabetes, type 2 diabetes, and gestational diabetes. Diabetes is a progressive disease in that the longer one has it, the more complications ensue. Therefore, it is helpful to conceptualize diabetes as a process that can be stopped, but not reversed. Research that contributes to slowing down or stopping the process can be extremely valuable to global health regardless of its contribution to cure and prevention because of the astronomical rates of diabetes in our world today. 

Inflammation is a strong indicator of diabetes development and progression. Inflammation predicts the development of diabetes [@freemanCreactiveProteinIndependent2002] [@10.1161/01.cir.103.3.357] [@schmidtMarkersInflammationPrediction1999]. Specifically, trials for drugs directed at inflammation among people with type 2 diabetes have indicated that drugs targeted at inflammation may be a therapeutic option for preventing diabetes [@10.4239/wjd.v5.i5.697].Retinopathy and focal neuropathy [@saidDiabeticNeuropathyReview2007] have also been linked to inflammatory processes. Additionally, the direct damage caused by high blood glucose leads to more inflammation and creates a nasty feedback loop wherein inflammation causes more insulin resistance which leads to high blood glucose. 

Diabetes treatment and inflammation

The ability of cells to absorb insulin can be increased through diet, exercise, and oral pills.Increasing exercise and dieting can cause major decreases in inflammation. Some of the drugs for type 2 diabetes aimed at increasing insulin sensitivity also decrease inflammation (e.g., drugs that cause weight loss). In the opposite direction, insulin can cause severe low blood glucose levels that initiate a stress response causing more inflammation.

# Methods

C-reactive protein and hba1c measured through dried bloodspots (minimally invasive biomarkers) [@10.1353/dem.2007.0038). 

Self-report surveys conducted by trained interviewers. 

Data are from the World Health Organization's Study on Adult Health and Ageing (SAGE). Our data is from 1 of 5 countries where the data were collected.

Cite R packages here

# Discussion 



## Limitations

We were not able to look at pills and insulin separately and some their effects have the potential to cancel each other out. The sex variable was established through interviewer discernment. 

# References