---
title             : "Relations between Inflammation and Access to care, Treatment, and Diabetes in Older Mexicans"
shorttitle        : "Inflammation, Access to care, and Treatment among Older Mexicans with Diabetes"

author: 
  - name          : "Dominik Grätz"
    affiliation   : "1"
    email         : "dgrtz@uoregon.edu"
  - name          : "Rachel Miller-Moudgil"
    affiliation   : "1"
    email         : "rmillerm@uoregon.edu"
  - name          : "Amber Somarriba"
    affiliation   : "1"
    email         : "asomarri@uoregon.edu"
  - name          : "Brittany Spinner"
    affiliation   : "1"
    email         : "bspinner@uoregon.edu"
  - name          : "Tian Walker"
    affiliation   : "1"
    email         : "twalker@uoregon.edu"

affiliation:
  - id            : "1"
    institution   : "University of Oregon"
    
authornote: "List of group members ordered by alphabet."

abstract: "Diabetes is a leading cause of death in Mexico and is closely linked to the obesity epidemic. Previous studies indicate that inflammation predicts the development of diabetes and is found to be a strong indicator of diabetes development and progression. However,  there are limited studies investigating the extent to which inflammation levels relate to the different treatment options among those with diabetes among Mexicans. To gain insight on the extent to which inflammation levels relate to medication, diet, and exercise we conducted a cross-sectional, secondary analysis using linear regression modeling and Chi-square tests of independence. Medication model fit parameter included (N = 357) F(2,354) = 1.06, p= 0.35, with R2= 0.01. Diet and exercise model fit parameters included (N= ) F(2, 354) = 2.70,p= 0.07 withR2= 0.02. And evaluating diet and exercise with access to care results included X2 results: X2(1) = 0.57, p= 0.45. Results indicate that among older Mexicans with diabetes there were no direct effects of treatment and access to inflammation levels."

keywords          : "Diabetes, access to care, inflammation, health, Mexico, China"
wordcount         : "X (this cannot easily be done automatically, we can also just leave it out)"

bibliography      : [references.bib]
link-citations    : true

floatsintext      : no
figurelist        : yes
tablelist         : yes
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = FALSE, warning = FALSE, echo = FALSE,  results='hide')
library(tidyverse)
library(rio)
library(here)
library(papaja)
library(janitor)
library(tidyr)
library(stargazer)
library(ggpubr)
library(psych)
library(gt)
source(file = here("scripts", "report_p.R"))
```


```{r data-cleaning-rachel, echo=FALSE}
#Rachel's code to drop irrelevant variables, filter, and add a medication*dt_exrcse variable.

data <- import(here("data","mexico_raw_dat.csv")) %>% as_tibble #Importing the Mexico dataset
data <- data %>% 
  select(sex, diagnosis, age, hba1c, crp, medication, dt_exrcse, q5026) %>% 
  rename(access = q5026) %>% 
  filter(age >=50 & diagnosis == 1 & crp < 5) %>% 
  as_tibble() #Selecting only relevant variables, renaming for clarification, and filtering for people with a diabetes diagnosis and high levels of inflammation (crp).
data <- data %>% 
  mutate(med_dt_exrcse = medication*dt_exrcse, .after=dt_exrcse) %>% 
  mutate(med_dt_exrcse = dplyr::recode(med_dt_exrcse, '4' = "1", '1' = "2", '2' = "2")) #Adding a new column for people who both take medication AND diet and exercise. 1 = yes for both, 2 = not yes for both
#making categorical variables factors
data <- data %>%
  mutate(sex = as.factor(sex),
         diagnosis = as.factor(diagnosis),
         medication = as.factor(medication),
         dt_exrcse = as.factor(dt_exrcse),
         med_dt_exrcse = as.factor(med_dt_exrcse),
         access = as.factor(access))
#For our own sanity, this is a mini dataframe of variables,  descriptions, and  coding criteria (if applicable). NOTE TO ALL: If you add any new variable to the dataset, please update this or let me know so I can update it! -Rachel
col1_var <- c("sex",
              "diagnosis",
              "age",
              "hba1c",
              "crp",
              "medication",
              "dt_exrcse",
              "med_dt_exrcse",
              "access",
              "num_care")
col2_desc <- c("participant gender (as reported by researcher)",
               "whether the participant has been diagnosed with diabetes",
               "participant age",
               "participant blood sugar level over the past 3 months",
               "participant inflammation level",
               "whether the participant is currently taking medication for diabetes inflammation",
               "whether the participant is on a diabetes-specific diet and exercise plan",
               "whether the participant is on BOTH medication and a diet and exercise plan",
               "whether the participant has accessed medical care in the past year",
               "number of times the participant has accessed medical care in the past year")
col3_code <- c("male = 1, female = 2",
               "yes = 1, no = 2", 
               "discrete variable",
               "continuous variable",
               "continuous variable",
               "yes = 1, no = 2",
               "yes = 1, no = 2",
               "yes = 1, no = 2",
               "yes = 1, no = 2",
               "discrete variable")
data_variables <- data.frame(col1_var, col2_desc, col3_code) %>% 
  rename("Variable name" = col1_var, "Description" = col2_desc, "Coding criteria" = col3_code)

```


```{r variables-table}
#data_variables
```

```{r data-cleaning-tian2}
data <- data %>% 
  mutate(diabetes_treat=case_when(
    medication== 1  ~ "medication",
    dt_exrcse==1 ~ "dt_excercise",
    medication == 2  & dt_exrcse == 2 ~ "no_treatment")) %>%
  mutate(diabetes_stat=case_when(
    hba1c >= 6.5 & diagnosis==2 ~ "undiagnosed",
    diagnosis==1 ~ "diagnosed",
    hba1c < 6.5  ~ "no_diabetes"))

#raw data for graphing purposes
dat <- import(here("data","mexico_raw_dat.csv")) %>% as_tibble

dat <- dat %>% 
  mutate(diabetes_treat=case_when(
    medication== 1  ~ "medication",
    dt_exrcse==1 ~ "dt_excercise",
    medication == 2  & dt_exrcse == 2 ~ "no_treatment"))
#data <- data %>% 
# filter(diabetes_treat != "no_treatment" & hba1c < 6.5)
#This above code filter isn't filtering the "and" with each line of data but first filtering all of those that don't equal no treatment and then filtering out everyone with an hba1c below 6.5...which is not what we want 
#So I made a new variable that we can use to filter:
data <- data %>% 
  mutate(treatment_info = if_else(diabetes_treat == "no_treatment" & hba1c < 6.5, "unknown_treat", "known_treat"))
#This graph is to check that the correct data points were coded for and can be filtered out. It looks good. 
#data %>% 
#  ggplot(aes(hba1c, crp)) + geom_point(aes(color = treatment_info)) 
data <- data %>% 
  filter(treatment_info == "known_treat")
#table(data$treatment_info)  #check to be sure that the filter worked. It looks good


dat <- dat %>%
  mutate(diabetes_stat=case_when(
    hba1c >= 6.5 & diagnosis==2 ~ "undiagnosed",
    diagnosis==1 ~ "diagnosed",
    hba1c < 6.5  ~ "no_diabetes"))


dat <- dat %>%
  mutate(a1c_dichot_words = ifelse(hba1c>= 6.5, "elevated", "in_range")) 

data <- data %>%
  mutate(a1c_dichot_words = ifelse(hba1c>= 6.5, "elevated", "in_range")) 
```

```{r data-cleaning-tian2-fig, fig.cap = "(ref:data-cleaning-tian2-fig)", include=FALSE}
# I wasn't sure if you wanted this figure to be in the knitted document, so I added it to this chunk so that we can have it here but now show it! 
data %>% 
  ggplot(aes(hba1c, crp)) + geom_point(aes(color = treatment_info))


#(ref:data-cleaning-tian2-fig) Figure caption goes here.
```

```{r, plot-all, fig.cap = "(ref:plot-all)"}
(plot_all <- dat %>% 
   mutate(diabetes_stat = recode(diabetes_stat, "diagnosed" = "Diagnosed", "no_diabetes" = "No Diabetes", "undiagnosed" = "Undiagnosed")) %>%
   filter(!is.na(diabetes_stat)) %>% 
   ggplot(aes(hba1c,crp))  + 
   labs(title = "Relationship between CRP and HbA1c by Medication for Diagnosis", x = "HbA1c", y = "CRP")+
   geom_point(aes(color = as.factor(medication )) )+ 
   facet_wrap(~diabetes_stat) +
   theme_apa() +
   scale_color_manual(values = c("tomato1", "purple4"), name = "Medication?", labels = c("Yes", "No", "N/A")))

```

(ref:plot-all) Figure caption goes here.

```{r, plot-all2, fig.cap = "(ref:plot-all2)"}

(plot_all2 <- dat %>% 
   filter(crp <5, age > 50) %>% 
   filter(!is.na(diabetes_treat)) %>% 
   ggplot(aes(hba1c, crp)) + geom_point(aes(color = diabetes_treat), size = 3) + 
   geom_vline(xintercept = 6.5, color = "dodgerblue")+ 
   scale_color_brewer(palette = 15, name = "Type of Treatment", labels = c("Diet & Exercise", "Medication", "No Treatment")) + 
   theme_apa() + 
   labs(title = "The Relationship Between Inflammation and HbA1c by Diabetes Treatment", caption = "dark green points should not be there",
        x = "HbA1c",
        y = "Inflammation (CRP)"))

```

(ref:plot-all2) Figure caption goes here.

```{r, tian-fig-hba1c-65, fig.cap = "(ref:tian-fig-hba1c-65)"}

#this is a check to see that the code above worked. It did! (which we know because the dark green - no treatment category is removed from the plot below 6.5 but remain above 6.5)
#AND it is super interesting to see what is left behind! only 3 data points in this group of people with healthy blood sugar levels were doing diet and exercise. 

plot.all_filtered <- data %>% 
  filter(crp <5, age > 50) %>% 
  ggplot(aes(hba1c, crp)) + 
  geom_point(aes(color = diabetes_treat), size = 3) +
  geom_vline(xintercept = 6.5, color = "darkorchid4") +
  scale_color_brewer(palette = 11, name = "Diabetes Treatment", labels = c("Diet & Exercise", "Medication", "No Treatment")) 

plot.a <- data %>% 
  filter(crp <5, age > 50) %>% 
  ggplot(aes(hba1c, crp)) + geom_point(aes(color = diabetes_treat), size = 3) +
  theme_apa() +
  scale_color_brewer(palette = 11, name = "Diabetes Treatment", labels = c("Diet & Exercise", "Medication", "No Treatment")) + 
  theme_apa()

(tian_hba1c_65 <- plot.a + 
    font("xlab", size = 14) + font("ylab", size = 14)+
    font("xy.text", size = 14, color = "black", face = "bold") +
    labs( title = "Relationship Between CRP and HbA1c by Diabetes Treatment", 
          caption =  "Note that all data points with No Treatment were removed from below HbA1c 6.5", 
          x = "HbA1c", 
          y = "Inflammation (CRP)") + 
    theme_apa())

```

(ref:tian-fig-hba1c-65) Here goes the caption.


```{r pivot-group_by}
#Code to fulfill all of Joe's requirements.
#pivot_wider, to investigate crp levels by sex
crp_by_sex <- data %>% pivot_wider(names_from="sex", values_from="crp") %>% rename(male="1",female="2") %>% as_tibble
#pivot_longer, to investigate medication by crp level
medication_by_crp <- data %>% pivot_longer(cols = "crp", "medication", values_to = "crp","on medication?", names_repair = "unique") #This isn't really doing what I want it to, but I'm out of time for now. -Rachel
#group_by, to look at the mean crp of participants who both take medicine and diet and exercise, versus those who don't.
groups_med_dt_exrcse <- data %>%
  group_by(medication, dt_exrcse) %>% 
  dplyr::summarize(mean = mean(crp)) %>% 
  as_tibble()
```

```{r crp-by-sex-male, fig.cap="(ref:crp-by-sex-male)"}
#include this in final product
crp_by_sex %>% 
  ggplot(aes(diabetes_treat, male)) + 
  geom_col(aes(fill = a1c_dichot_words), position = "dodge") +
  labs(x = "Diabetes Treatment",
       y = "CRP Level (Male)",
       title = "Diabetes Treatment and Male CRP by HbA1c")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = c("Diet & Exerc.", "Medication", "No Treatment"))+
  scale_fill_brewer(palette = "Blues", name = "HbA1c Levels", labels = c("Elevated", "In Range"))+
  theme_apa()
```

(ref:crp-by-sex-male) Here goes the caption.


```{r crp-by-sex-female, fig.cap="(ref:crp-by-sex-female)"}
#include this in final product
crp_by_sex %>% 
  ggplot(aes(diabetes_treat, female)) + 
  geom_col(aes(fill = a1c_dichot_words), position = "dodge")+
  labs(x = "Diabetes Treatment",
       y = "CRP Level (Female)",
       title = "Relationship Between Diabetes Treatment and Female CRP by HbA1c")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = c("Diet & Exerc.", "Medication", "No Treatment"))+
  scale_fill_brewer(palette = "RdPu", name = "HbA1c Levels", labels = c("Elevated", "In Range"))+
  theme_apa()
```

(ref:crp-by-sex-female) Here goes the caption.

```{r RQ1, render = 'normal print'}
#RQ1: Does taking medication lower inflammation levels? (Requires filtering, modeling, a table, and a figure. Do only as much as possible in this timeframe!)
RQ1_df <- data %>% 
  filter(!is.na(medication) & !is.na(age) & !is.na(crp))
mreg1 <- lm(crp~age + medication, data = RQ1_df)
#summary(mreg1) #No significant findings. Oh well!
#mreg1_plot <- ggplot(RQ1_df, aes(medication, hba1c, age)) + geom_point() + stat_smooth(method = "lm", formula = mreg1, geom = "smooth") #This plot looks terrible right now, so I will see if we need to come back to it later.
#table(data$medication) #this a quick way to see the n in both categories
```

```{r, RQ1plot, fig.cap = "(ref:RQ1plot)"}
RQ1_df %>% 
  ggplot(aes(age, crp)) + 
  geom_point(aes(color = medication), alpha = 0.5) + 
  geom_smooth(aes(color = medication), method = "lm", se = FALSE) + 
  scale_color_brewer(palette = 11, name = "Taking Medication?", labels = c("Yes", "No")) + 
  theme_apa() + 
  labs( title = "Age and Inflammation by Medication", 
        caption =  "SAGE data from Mexico", 
        x = "Age", 
        y = "Inflammation (CRP)")
```

(ref:RQ1plot) Here goes the caption.

```{r, tian-filtering, fig.cap = "(ref:tian-filtering)"}
#This visualization is the one that alerted me to the fact that my original attempt at filtering had removed all data above 6.5. We 
dat %>% 
  filter(diabetes_treat != "no_treatment" & hba1c < 6.5) %>% 
  filter(medication != 0) %>% 
  ggplot(aes(hba1c, crp)) + 
  geom_point(aes(color = diabetes_treat), alpha = 0.5) + 
  geom_smooth(aes(color = medication), method = "lm", se = FALSE, color = "gray") + 
  #scale_color_brewer(palette = 14, name = "Diabetes Treatment", labels = c("Diet & Exercise", "Medication")) + 
  theme_apa() +
  labs( title = "Blood Sugar and Inflammation by Treatment", 
        caption =  "SAGE data from Mexico", 
        x = "HbA1c", 
        y = "Inflammation (CRP)") +
  scale_color_manual(name = "Diabetes Treatment", labels = c("Diet & Exercise", "Medication"), values = c("magenta", "limegreen"))
#scale_color_brewer(  name = "Diabetes Treatment", labels = c("Diet & Exercise", "Medication")) 

#change colors freely. none of the palettes are working 

#this line does not enable manual color adjustment
```

(ref:tian-filtering) Here goes the caption.



```{r regtab1, results='asis'}
mreg1_summary<- summary(mreg1)
table1 <- apa_print(mreg1)
table1$table$predictor <- c('Intercept', 
                            'Age',
                            'Medication')

colnames(table1$table)[1] <- "Predictor"

apa_table(table1$table,
          caption = "Effect of Medication on CRP, controlling for Age. ",
          note = paste0("Model fit: $F$(", mreg1_summary$fstatistic[2], ", ", mreg1_summary$fstatistic[3], ") = ", round(mreg1_summary$fstatistic[1], 2), ", $p$ ", report_p(get_model_p(mreg1_summary)), ", $R^2$ = ", round(mreg1_summary$r.squared, 2), "."))
mreg1_N <- nrow(RQ1_df)
#gets us the reg weights
mreg1_inter <- mreg1_summary$coefficients[1, 1] %>% round(3)
mreg1_age <- mreg1_summary$coefficients[2, 1] %>% round(3)
mreg1_med <- mreg1_summary$coefficients[3, 1] %>% round(3)
#gets us the standard errors
mreg1_inter_se <- mreg1_summary$coefficients[1, 2] %>% round(3)
mreg1_age_se <- mreg1_summary$coefficients[2, 2] %>% round(3)
mreg1_med_se <- mreg1_summary$coefficients[3, 2] %>% round(3)
#gets us the p values (the output is a string that uses conventions in reporting p values)
mreg1_inter_p <- mreg1_summary$coefficients[1, 4] %>% report_p()
mreg1_age_p <- mreg1_summary$coefficients[2, 4] %>% report_p()
mreg1_med_p <- mreg1_summary$coefficients[3, 4] %>% report_p()
#F test of the entire model
mreg1_f <- mreg1_summary$fstatistic[1] %>% round(3)
mreg1_f_df1 <- mreg1_summary$fstatistic[2] %>% round(3)
mreg1_f_df2 <- mreg1_summary$fstatistic[3] %>% round(3)
mreg1_f_p <- report_p(get_model_p(mreg1_summary))
mreg1_r2 <- mreg1_summary$r.squared %>% round(3)
```

```{r RQ2, results='asis'}
#RQ2: Does diet and exercise predict inflammation levels? (Requires filtering, modeling, a table, and a figure. Do only as much as possible in this timeframe!)
RQ2_df <- data %>%
  filter(!is.na(dt_exrcse) & !is.na(age), !(is.na(crp)))
reg2 <- lm(crp ~ age + dt_exrcse, data = data)
#summary(reg2)
#stargazer(reg2, type = "text")
#Could not get the summary table to work! (AS)
reg2_summary <- summary(reg2)
table2 <- apa_print(reg2)
table2$table$predictor <- c('Intercept',
                            'Age',
                            'Diet and Exercise')

colnames(table2$table)[1] <- "Predictor"

apa_table(table2$table,
          caption = "Effect of Diet and Exercise on CRP, controlling for Age.",
          note = paste0("Model fit: $F$(", reg2_summary$fstatistic[2], ", ", reg2_summary$fstatistic[3], ") = ", round(reg2_summary$fstatistic[1], 2), ", $p$ ", report_p(get_model_p(reg2_summary)), ", $R^2$ = ", round(reg2_summary$r.squared, 2), "."))
#table(data$dt_exrcse) #this a quick way to see the n in both categories
reg2_N <- nrow(RQ2_df)
#gets us the reg weights
reg2_inter <- reg2_summary$coefficients[1, 1] %>% round(3)
reg2_age <- reg2_summary$coefficients[2, 1] %>% round(3)
reg2_de <- reg2_summary$coefficients[3, 1] %>% round(3)
#gets us the standard errors
reg2_inter_se <- reg2_summary$coefficients[1, 2] %>% round(3)
reg2_age_se <- reg2_summary$coefficients[2, 2] %>% round(3)
reg2_de_se <- reg2_summary$coefficients[3, 2] %>% round(3)
#gets us the p values (the output is a string that uses conventions in reporting p values)
reg2_inter_p <- reg2_summary$coefficients[1, 4] %>% report_p()
reg2_age_p <- reg2_summary$coefficients[2, 4] %>% report_p()
reg2_de_p <- reg2_summary$coefficients[3, 4] %>% report_p()
#F test of the entire model
reg2_f <- reg2_summary$fstatistic[1] %>% round(3)
reg2_f_df1 <- reg2_summary$fstatistic[2] %>% round(3)
reg2_f_df2 <- reg2_summary$fstatistic[3] %>% round(3)
reg2_f_p <- report_p(get_model_p(reg2_summary))
reg2_r2 <- reg2_summary$r.squared %>% round(3)
```

```{r RQ3-brittany}
#RQ3: Is there a relationship between seeing a doctor in the last year and using diet and exercise as a treatment for diabetes? 
# Null: There is no relationship between seeing a doctor in the last year and diet and exercise. 
# data <- import(here("data","mexico_raw_dat.csv")) %>% as_tibble #Importing the Mexico dataset #From Rachel: I'm hashtagging this out, because if you re-import the dataset here, it loses all the cleaning from earlier. 
#filter(!is.na(medication) | !is.na(hba1c) | !is.na(age) | !is.na(crp))
RQ3df <- data %>% 
  filter(!is.na(dt_exrcse) & !is.na(age) & !(is.na(crp)) & !is.na(access)) #From Rachel: There were inconsistencies from the cleaning to here about the variable being called care vs. access. I switched them all to access, here and in the code below.
RQ3df <- RQ3df %>% select(diagnosis, age, crp, dt_exrcse, access) %>%  
  filter(age >=50 & (diagnosis == 1 | crp < 5))
RQ3df$access <- factor(RQ3df$access,
                       levels = c(1,2), labels = c("Yes","No")) 
RQ3df$dt_exrcse <- factor(RQ3df$dt_exrcse, 
                          levels = c(1,2), labels = c("Yes", "No"))
prop <- prop.table(table(RQ3df$access))
prop2 <- prop.table(table(RQ3df$dt_exrcse))
prop
prop2
RQ3_barplot <- barplot(prop, xlab = "Saw a doctor in the last year Y/N", ylab = "Frequency", main = "Proportion of Individuals 50yrs or older with Diabetes who saw a Doctor in the Last Year ") #need to add title and subtitle(?)
RQ3_barplot
chi_df <- chisq.test(RQ3df$access, RQ3df$dt_exrcse)
chi_df
chi_df$expected
chi_df$observed 
#chi_df <- chisq.test(RQ3df$access, RQ3df$dt_exrcse)
#chi_df
#chi_df$expected
#chi_df$observed 

```

```{r, prop-access-bar, fig.cap = "(ref:prop-access-bar)"}
#RQ4: For those partaking in diet and exercise, what is the relation of visiting the doctor in the last year on inflammation levels?
#Null: There is no relation between visiting the doctor in the last year and inflamation levels among those that partake in diet and exercise as a treatment for diabetes. 
RQ4df <- data %>% 
  filter(!is.na(dt_exrcse) & !is.na(age) & !(is.na(crp)) & !is.na(access))

RQ4df <- RQ4df %>% select(diagnosis, age, crp, dt_exrcse, access) %>%  
  filter(age >=50 & (diagnosis == 1 | crp < 5) & dt_exrcse == 1)
RQ4df$access <- factor(RQ4df$access,
                       levels = c(1,2), labels = c("Yes","No")) 

#RQ4df$crp <- RQ4df %>% 
#factor(if_else(crp <= 3.0, "low", "high"), levels = c("low", "high"))

RQ4df <- RQ4df %>% 
  mutate(crp2 = factor(ifelse(crp <= 3.0, "low", "high"), levels = c("low", "high"))) 


tibble(RQ4df$access, RQ4df$crp2)

chi_df_access <- chisq.test(RQ4df$access, RQ4df$crp2)
chi_df_access
chi_df_access$expected
chi_df_access$observed 

#RQ4df$crp2 <- factor(RQ3df$crp2, 
#levels = c(1,2), labels = c("low", "high"))

prop_access_bar <- ggplot(data = RQ4df, aes(x = access, fill = crp2))+
  geom_bar(position = "dodge")+
  labs(title = "Relation of Inflamation Levels low/high and Seeing a Doctor in the Last Year Y/N", subtitle= "Among Individuals with Diabetes that use Diet and Exercise as Treatment", x = "Saw a doctor in the last year Y/N", y = "Frequency")
prop_access_bar+
  scale_fill_brewer(palette = "Spectral", name = "CRP Levels", labels = c("Low", "High"))

#prop4
#For those with vs. without access to medical care, what is the effect of diet and exercise on inflammation levels? 
```
(ref:prop-access-bar) Here goes the caption.

```{r descriptives table prep}
summary <- data %>%
  summarize(country = "Mexico",
            N = n(),
            N_male = sum(sex == 1, na.rm = TRUE), #1 is male
            N_male_pct = round((N_male/N*100), 1),
            N_female = sum(sex == 2, na.rm = TRUE),
            N_female_pct = round((N_female/N)*100, 1),
            N_unknown = sum(is.na(sex)),
            N_unknown_pct = round((N_unknown/N)*100, 1),
            diabetes_diag = sum(diagnosis == 1, na.rm = TRUE),
            diabetes_diag_pct = round((diabetes_diag/N)*100, 1),
            diabetes_undiag = sum(hba1c >= 6.5 & diagnosis == 2, na.rm = TRUE),
            diabetes_undiag_pct = round((diabetes_undiag/N)*100, 1),
            age_M = round(mean(age), 1),
            age_SD = round(sd(age), 1))

chi <- chisq.test(table(data$sex)) #why is this here? what is this asking? #just seeing if there is women are overrepesented in our sample.

```

```{r tableofcrpmedicationandexercise, fig.cap = "(ref:tableofcrpmedicationandexercise)"}
ggplot(groups_med_dt_exrcse, aes(medication, mean))+
  theme_apa()+
  geom_col(aes(fill = dt_exrcse),
           position = "dodge")+
  labs(x = "Medication",
       y = "Mean CRP Level",
       title = "Mean CRP levels for medication and exercise groups")+
  scale_x_discrete(labels=c("Medication", "No Medication"))+
  scale_fill_manual(name = "Exercise", labels = c("Yes", "No"), values = c("#d4b9da", "#c994c7"))
```


```{r include=FALSE}
#code for appendix exploration 

#rename variables of interest from the Health State Description Scale 
dat <- dat %>% 
  rename(activities = q2001, vigorous_act = q2003, bod_discomfort = q2008, walking = q2026, standing = q2028, picking_up = q2031 )


#select variables of interest and create a new data frame(df) that can be manipulated.

dat2 <- dat %>% 
  select(id, crp, hba1c, age, activities, vigorous_act, bod_discomfort, walking, standing, picking_up, diabetes_treat, diagnosis, medication, dt_exrcse) %>% 
  #remove codes that indicate na variables from any variables that have them (checked by looking at min and max through the describe function)
  filter(walking != 8 & walking != 9) %>% 
  filter(standing != 8 & standing != 9) %>% 
  filter(picking_up != 8 & picking_up != 9)

#move the diabetes variable into the new df
dat2 <- dat2 %>% 
  mutate(diabetes=if_else(diagnosis ==1|hba1c >6.5,"yes","no"))


#move the diabetes levels variable into the new df
dat2 <- dat2 %>% 
  mutate(levels_dbts =
           case_when(
             diabetes == "yes" & medication == 1 & dt_exrcse == 1 ~ "treated_diabetes",
             diabetes == "yes"& medication == 2 & dt_exrcse == 2  ~ "untreated_diabetes",
             diabetes == "no" ~ "no_diabetes", 
             hba1c > 6.5 & diagnosis == 2 ~ "undiagnosed_diabetes"))

#move the dichotomized hba1c variable into the new df
dat2 <- dat2 %>% 
  mutate(a1c_dichot_words = ifelse(hba1c>= 6.5, "elevated", "in_range")) 
dat2

#this is where I checked to be sure the values make sense
describe(dat2$activities)
describe(dat2$vigorous_act)
describe(dat2$bod_discomfort)
describe(dat2$walking)
describe(dat2$standing)
describe(dat2$picking_up)

```

```{r appendix-fig1, fig.cap = "(ref:appendix-fig1)"}
dat2_long <- dat2 %>% 
  pivot_longer(cols = 5:10, names_to = "health_state_vars", values_to = "hs_score")

dat2_long %>% 
  filter(!is.na(levels_dbts)) %>% 
  filter(crp < 5) %>% 
  group_by(id) %>% 
  summarize(mean_hs = mean(hs_score, na.rm = TRUE), crp, levels_dbts, a1c_dichot_words) %>% 
  ggplot(aes(mean_hs, crp)) + geom_point(aes(color = levels_dbts)) + geom_smooth(aes(color = levels_dbts), method = "lm") + scale_color_brewer(type = "div", palette = 4, name = "Diabetes Level", labels = c("No Diabetes", "Treated Diabetes", "Undiagnosed Diabetes", "Untreated Diabetes")) + labs(title = "CRP and Health Score by Diabetes", caption = "Health score is calculated such that higher scores = worse health", x = "Mean Health Score", y = "Inflammation (CRP) Levels")+
  theme_apa()

```

(ref:appendix-fig1) Here goes the caption.

```{r eval=FALSE, appendix-fig2, fig.cap="(ref:appendix-fig2)", include=FALSE}
#Why is this repeated?
#pivoting the data
dat2_long <- dat2 %>% 
  pivot_longer(cols = 5:10, names_to = "health_state_vars", values_to = "hs_score")

#creating summaries and graphing 
dat2_long %>% 
  filter(!is.na(levels_dbts)) %>% 
  filter(crp < 5) %>% 
  group_by(id) %>% 
  summarize(mean_hs = mean(hs_score, na.rm = TRUE), crp, levels_dbts, a1c_dichot_words) %>% 
  ggplot(aes(mean_hs, crp)) + geom_point(aes(color = levels_dbts)) + geom_smooth(aes(color = levels_dbts), method = "lm") + scale_color_brewer(type = "div", palette = 4, name = "Diabetes Level", labels = c("No Diabetes", "Treated Diabetes", "Undiagnosed Diabetes", "Untreated Diabetes")) + labs(title = "CRP and Health Score by Diabetes", caption = "Mean health score is calculated such that higher scores = worse health", x = "Mean Health Score", y = "Inflammation (CRP) Levels") + theme_apa()

```

(ref:appendix-fig2) Here goes the caption.

```{r}
#Table summarizing the data in the graph
dat2_long_neat <- dat2_long %>% 
  filter(!is.na(levels_dbts)) %>% 
  filter(crp < 5) %>% 
  group_by( levels_dbts, health_state_vars) %>% 
  summarize(mean_crp = mean(crp, na.rm = TRUE), mean_score = mean(hs_score))%>% 
  gt()
```

```{r appendix-fig3, fig.cap="(ref:appendix-fig3)"}
dat2_long %>% 
  filter(!is.na(diabetes_treat)) %>% 
  filter(!is.na(a1c_dichot_words)) %>% 
  filter(crp < 5) %>% 
  group_by(id) %>% 
  mutate(diabetes_treat = recode(diabetes_treat, "dt_excercise" = "Diet & Exercise", "medication" = "Medication", "no_treatment" = "No Treatment")) %>% 
  summarize(mean_hs = mean(hs_score, na.rm = TRUE), crp, diabetes_treat, a1c_dichot_words) %>% 
  ggplot(aes(mean_hs, crp)) + geom_col(aes(fill= a1c_dichot_words, position = "dodge"), method = "lm") + facet_wrap(~diabetes_treat) + scale_fill_manual(values = c("salmon","springgreen"), name = "HbA1c Levels", labels = c("Elevated", "In Range"))+
  theme_apa()+
  theme(plot.title = element_text(hjust = 0.5))+
  labs(title = "CRP Frequency and Health Score by HbA1c for Treatment Groups",
       x = "Mean Health Score",
       y = "CRP Frequency")

```

(ref:appendix-fig3) Here goes the caption.

```{r, appendix-fig4, fig.cap="(ref:appendix-fig4)"}
#a glimpse at what is going on with hba1c 
dat2_long %>% 
  filter(!is.na(diabetes_treat)) %>% 
  group_by(id) %>% 
  summarize(mean_hs = mean(hs_score, na.rm = TRUE), hba1c, diabetes_treat) %>% 
  ggplot(aes(mean_hs, hba1c)) + geom_point(aes(color = diabetes_treat)) + geom_smooth(aes(color = diabetes_treat), method = "lm") + labs(title = "HbA1c and Mean Health Score by Treatment", x = "Mean Helth Score", y = "HbA1c") +
  scale_color_brewer(palette = 3, name = "Diabetes Treatment", labels = c("Diet & Exercise", "Medication", "No Treatment")) +
  theme_apa()
```

(ref:appendix-fig4) Here goes the caption.


(ref:tableofcrpmedicationandexercise) Here goes the caption.


|  |            |`r summary$country[1]` |
|:-|:-----------|:----------------------|
|$N_{total}$|           |`r summary$N[1]`                                                     |
|Sex        |           |                                                                     |
|           |male       |`r summary$N_male[1]` (`r summary$N_male_pct[1]` %)                  |
|           |female     |`r summary$N_female[1]` (`r summary$N_female_pct[1]` %)              |
|           |unknown    |`r summary$N_unknown[1]` (`r summary$N_unknown_pct[1]` %)            |
|Age        |           |`r summary$age_M[1]` ($SD$ = `r summary$age_SD[1]`)                  |

Table: (\#tab:descriptives) Descriptive statistics.

```{r}
mex_sub_plota <- dat%>%
  filter(!is.na(diabetes_stat))%>%
  filter(!is.na(hba1c)) %>%
  filter(crp<5) %>%
  group_by(diabetes_stat) %>%
  summarise( mean_hba1c = mean(hba1c), se_hba1c = sqrt(var(hba1c, na.rm = TRUE) / 
                                                         length(na.omit(hba1c))))

dshba1c <- mex_sub_plota %>%
  ggplot(aes(x = as.factor(diabetes_stat), y = mean_hba1c)) + 
  geom_col(aes(fill = diabetes_stat), color = "black") + 
  geom_errorbar(aes(ymax = mean_hba1c + se_hba1c, 
                    ymin = mean_hba1c - se_hba1c), width=.1) +
  scale_fill_brewer(palette = 11) + 
  labs(
    title = "Mean HbA1c and Diabetes Status in Mexico",
    
    caption = "Figure 5", x = "Diabetes Status", y = "Mean CRP", fill = "Diabetes Status")+
  theme_apa()

```

```{r, dshba1c, fig.cap="(ref:dshba1c)"}
(dshba1c)
```

(ref:dshba1c) Here goes the caption.

```{r  ds-crp}
mex_sub_plot <- dat%>%
  filter(!is.na(diabetes_stat))%>%
  filter(crp<5) %>%
  group_by(diabetes_stat) %>%
  summarise(mean_crp = mean(crp), se_crp = sqrt(var(crp, na.rm = TRUE) / 
                                                  length(na.omit(crp))))

dscrp <- mex_sub_plot %>%
  ggplot(aes(x = as.factor(diabetes_stat), y = mean_crp)) + 
  geom_col(aes(fill = diabetes_stat), color = "black") + 
  geom_errorbar(aes(ymax = mean_crp + se_crp, 
                    ymin = mean_crp - se_crp), width=.1) +
  scale_fill_brewer(palette = 10) + 
  labs(
    title = "Mean CRP and Diabetes Status in Mexico",
    
    caption = "Figure 4", x = "Diabetes Status", y = "Mean CRP", fill = "Diabetes Status") +
  theme_apa()
```

```{r, dscrp, fig.cap="(ref:dscrp)"}
(dscrp)
```

(ref:dscrp) Here goes the caption.

```{r}
mex_sub_plot6 <- dat %>%
  filter(!is.na(diabetes_treat))%>%
  filter(crp<5) %>%
  group_by(diabetes_treat) %>%
summarise( mean_crp = mean(crp), se_crp = sqrt(var(crp, na.rm = TRUE) / 
                                  length(na.omit(crp))))


treat_fig <- mex_sub_plot6 %>%
ggplot(aes(x = as.factor(diabetes_treat), y = mean_crp)) + geom_col(aes(fill = diabetes_treat), color = "black") + 
  geom_errorbar(aes(ymax = mean_crp + se_crp, 
                    ymin = mean_crp - se_crp), width=.1) +
  scale_fill_brewer(palette = 10) + theme_bw() + labs(
    title = "Mean CRP and Diabetes Treatment in Mexico",
    caption = "Figure 7", x = "Diabetes Treatment", y = "Mean CRP", fill = "Diabetes Treatment")

```

```{r, treat-fig, fig.cap="(ref:treat-fig)"}
(treat_fig)
```

(ref:treat-fig) Here goes the caption.

# FIGURE REFERENCES TO COPY

Figure \@ref(fig:plot-all)
Figure \@ref(fig:plot-all2)
Figure \@ref(fig:tian-fig-hba1c-65)
Figure \@ref(fig:crp-by-sex-male)
Figure \@ref(fig:crp-by-sex-female)
Figure \@ref(fig:RQ1plot)
Figure \@ref(fig:tian-filtering)
Figure \@ref(fig:prop-access-bar)
Figure \@ref(fig:tableofcrpmedicationandexercise)
Figure \@ref(fig:appendix-fig1)
Figure \@ref(fig:appendix-fig2)
Figure \@ref(fig:appendix-fig3)
Figure \@ref(fig:appendix-fig4)
Figure \@ref(fig:dshba1c)
Figure \@ref(fig:dscrp)
Figure \@ref(fig:treat-fig)

# TABLE REFERENCES TO COPY

Table \@ref(tab:regtab1) (Regression Table 1)

Table \@ref(tab:RQ2) (Regression Table 2)

Table \@ref(tab:descriptives) (Descriptives Table)


# Introduction

Diabetes and its insidious complications continue to expand as a global health burden at an alarming rate. In 2021, there were approximately 537 million adults living with diabetes in the world and this number is expected to jump to 783 million by 2045. A disproportionate percentage of these people live in low to middle income countries (LMICs). Given this predicted jump in incidence and in light of the COVID-19 pandemic, there is a heightened need in better understanding diabetes. During COVID-19, diabetes was found to both increase the severity of COVID-19 symptoms (in people with elevated a1c levels) and increase in incidence [@yangPrevalenceComorbiditiesIts2020] [@rohmInflammationObesityDiabetes2022]. Additionally, diabetes is associated with a steep increase in cardiovascular disease risk and is a leading cause of death in many low to middle income countries (LMICs) including Mexico. 

Although the precise classification of diabetes remains controversial because of the complex nature of its pathogenesis, there are three universally acknowledged subtypes: type 1 diabetes, type 2 diabetes, and gestational diabetes. Diabetes is a progressive disease in that the longer one has it, the more complications ensue. Therefore, it is helpful to conceptualize diabetes as a process that can be stopped, but not reversed. Research that contributes to slowing down or stopping the process can be extremely valuable to global health regardless of its contribution to cure and prevention because of the astronomical rates of diabetes in our world today. 

Research shows that inflammation predicts the development of diabetes and is found to be a strong indicator of diabetes development and progression.[@freemanCreactiveProteinIndependent2002] [@10.1161/01.cir.103.3.357] [@schmidtMarkersInflammationPrediction1999]. Specifically, trials for drugs directed at inflammation among people with type 2 diabetes have indicated that drugs targeted at inflammation may be a therapeutic option for preventing diabetes [@10.4239/wjd.v5.i5.697]. In addition, retinopathy and focal neuropathy [@saidDiabeticNeuropathyReview2007] have also been linked to inflammatory processes. Conversely, when left untreated, the direct damage caused by high blood glucose leads to more inflammation and creates a nasty feedback loop wherein inflammation causes more insulin resistance which leads to high blood glucose. Furthermore, it has been found that the ability of cells to absorb insulin can be increased through diet, exercise, and oral pills. 

A current gap in literature exists investigating the relationship between inflammation levels and the different treatments offered to those with diabetes, such as diet, exercise, and medication. This study seeks to fill this gap by investigating the extent to which inflammation levels relate to medication and diet and exercise among older Mexicans with diabetes.

# Methods
## Data
To examine the extent to which inflammation relates to medication, diet, and exercise among older Mexicans, we performed secondary data analyses using the two datasets from from the Wave 1 Study on Global Ageing (SAGE) from the World Health Organization (WHO). Cross-sectional baseline data was originally collected in 2016 through in-person interviews lasting on average between 90-120 minutes among Mexicans (age range) in Mexico. 

## Procedures and Sample

`r summary$N` participants were included in our analyses. Of those, `r summary$N_male` were assessed to be male (`r summary$N_male_pct` %), `r summary$N_female` were identified to be female (`r summary$N_female_pct` %). Sex data for `r summary$N_unknown` participant was missing (see Table \@ref(tab:descriptives)). This indicates that females were overrepresented in our sample, assuming binary sexes are represented equally in the population ($\chi^2$(`r chi$parameter`) = `r chi$statistic`, $p$ `r report_p(chi$p.value)`). The age in our sample was $M$ = `r summary$age_M` years (SD = `r summary$age_SD` years).
Because of missing values in the variables of interest in some of our analyses, subjects were excluded. Thus, $N$ is reported separately for each analysis.

## Variables

The original WHO dataset contains more than 1,600 variables, not all of which are relevant to our research questions. Therefore, we have limited our analysis to 10 variables, listed below in Table 1. In our analysis, we only included participants who reported that they already have a formal diabetes diagnosis from a doctor, since our research questions revolve around diabetes treatments. Figure (plot_all) shows the raw data and the data that we selected for our analysis (the colorful points on the far left).  


### Filtering

A variable was created called "diabetes treatment" wherein anyone who answered yes to 

[edit this to describe the three we use in our analysis]
A variable was created to indicate whether or not someone fell into one of the four following categories: diagnosed and treated diabetes, diagnosed and untreated diabetes, undiagnosed diabetes, or no diabetes. This variable was created using 3 questions from the in-person survey portion of the study. If participants answered yes to "Have you ever been diagnosed with diabetes (high blood sugar)?" and also answered yes to either "Have you been taking insulin or other blood sugar lowering medications in the last 2 weeks?" or "Have you been following a special diet, exercise regime or weight control program for diabetes during the last 2 weeks?", then they were in the diagnosed and treated group (China: n = 448, Mexico: n = 165). If they answered yes to diagnosis, but no to both treatment questions then they were placed in the untreated diabetes group (China: n = 43, Mexico: n = 39). If they answered no to the diagnosis question and their HbA1c was under 6.5% then they were placed in the no diabetes group (China: n = 5,246, Mexico: n = 1,241). Lastly, if they answered no to the diagnosis question but their HbA1c was 6.5% or higher, then they were placed into the undiagnosed diabetes group (China: n = 444, Mexico: n = 181). There was a group of people in both countries who answered "no" to both treatment options but still had an HbA1c level below 6.5% (China: n = 29, Mexico: n = 17). These people were excluded from the analysis. 


[This is good as is]
A variable was then created that indicated "unknown treatment" if the diabetes treatment variable indicated that there was no treatment but hba1c was below 6.5 and otherwise "Known treatment" was indicated. All "unknown treatment" variables were then removed (n = 17). See plot.all2 and plot.all_filtered to see the data before and after these data points were filtered out. 


### Biomarkers

Biomarkers.A subset of people participating in the SAGE study underwentbiomarker analysis in Mexico (n = 1831) and in China (n = 12,077). Exclusions included## people for incomplete data, ### people for having an elevated CRP value that might indicate injury or infection. The sample was ##% female and ##% male. Participant ages for this analysis ranged from 50 to 105 years old (M = 68.27, SD = 9.23).


Biomarkers were analyzed using dried blood spot (DBS) procedures, and collected via standard venipuncture into an EDTA tube. In order to go from venous blood to DBS, the samples of whole blood were homogenized and then pipetted in 20uL aliquots onto standard Whatman 903 filter paper. The samples were left to dry for 24 hours at room temperature before they were analyzed. We punched out a 6mm spot from the DBS card and used 250 uL of PBS buffer pH = 7 to elute for 14 hours. The Abbott Architect CI8200 chemistry analyzer was used to analyzed the DBS eluates in order to obtain CRP values and it was used for HbA1c as well. 

Hemoglobin A1c (HbA1c) is a measure of average blood glucose values over the past 3 months. HbA1c also required a 6 mm DBS punch. This one was eluted in 400uL MULTIAGEN Hemoglobin Denaturant for 14 hours. The Architect blood chemistry analyzer was loaded with a cuvette with eluent and was then used to determine HbA1c and total hemoglobin by measuring absorbance at 700 for Hba1cnm and 604nm for total hemoglobin. The analyzer's program calculated percent HbA1c using the following formula:[(HbA1c/TotHb)×100] - 3+(0.2 × TotHb).



Self-report surveys conducted by trained interviewers. 

Data are from the World Health Organization's Study on Adult Health and Ageing (SAGE). Our data is from 1 of 5 countries where the data were collected.

All analyses were conducted in R with the following packages: 
here [@here], rio[@chanRioSwissarmyKnife2021], tidyverse[re], ggpubr [@kassambaraGgpubrGgplot2Based2022],bibtex [@francoisBibtexBibtexParser2022],papaja [@austPapajaPrepareReproducible2022], psych
[@revellePsychProceduresPsychological2022],and forcats [@wickhamForcatsToolsWorking2022].


# Results

We see the expected relationships between diabetes status and HbA1c (see Figure \@ref(fig:dshba1c)). However, with CRP we see a relatively similar level of CRP between people without diabetes and those with diagnosed diabetes (see Figure \@ref(fig:dscrp)). Thus, we explored whether medication may be responsible for lowering CRP. In Figure \@ref(fig:treat-fig) we see that those who are using diet and exercise as treatment have higher CRP levels than those taking medication and those not on treatment. We explored this further statistically.  







## Regression 1
For our first research question, does taking medication lower inflammation levels, we found that this regression model (Table \@ref(tab:regtab1)) using `r mreg1_N` participants was not significant $F$(`r mreg1_f_df1`, `r mreg1_f_df2`) = `r mreg1_f`, $p$ `r mreg1_f_p` with $R^2$ = `r mreg1_r2`. The regression coefficient for age was $b_{age}$ = `r mreg1_age` ($SE$ = `r mreg1_age_se`, $p$ `r mreg1_age_p`), and for use of medication $b_{medication}$ = `r mreg1_med` ($SE$ =  `r mreg1_med_se`, $p$ `r mreg1_med_p`). Therefore, based on these results we fail to reject our null hypothesis and we cannot conclude that there is a relationship between medication and inflammation levels on average in this population. 

## Regression 2

Our research question two looked at diet and exercise as a treatment for diabetes on predicting inflammation levels. We found that this regression model  (Table \@ref(tab:RQ2)) using `r reg2_N` participants was not significant $F$(`r reg2_f_df1`, `r reg2_f_df2`) = `r reg2_f`, $p$ `r reg2_f_p` with $R^2$ = `r reg2_r2`. The regression coefficient for age was $b_{age}$ = `r reg2_age` ($SE$ = `r reg2_age_se`, $p$ `r reg2_age_p`), and for diet and exercise $b_{Diet}$ = `r reg2_de` ($SE$ =  `r reg2_de_se`, $p$ `r reg2_de_p`). Based on these results, fail to reject our null hypothesis and conclude that diet and exercise does not predict inflammation levels on average in this population. 

## Chi Square Test
To better understand differences in outcomes in health among those partaking in diet and exercise versus those that are not to treat diabetes, we seek to understand if there is difference in those that accessed health care in the last year and those that use diet and exercise as a treatment option for diabetes. $\chi^2$ results: ($\chi^2$(`r chi_df$parameter`) = `r chi_df$statistic`, $p$ `r report_p(chi_df$p.value)`). Based on these results we fail to reject the null hypothesis, and cannot conclude seeing a doctor in the last year relates to individuals using diet and exercise as treatment for diabetes in this population sample. 

Looking at individuals who partake in diet and exercise only as a treatment for diabetes, we seek to answer the extent to which seeing a doctor in the last year relates to inflammation levels. $\chi^2$ results: ($\chi^2$(`r chi_df_access$parameter`) = `r chi_df_access$statistic`, $p$ `r report_p(chi_df_access$p.value)`). Based on these results, we fail to reject our null hypothesis and cannot conclude that seeing a doctor in the last year relates to inflammation levels in this populaiton sample. 

# Discussion 

We see diet and exercise predicting CRP over and above the effects of age such that those who said that they do diet and exercise (insert direction based in RQ2 results). 

Ultimately we see that inflammation is impacted by diabetes treatments. Access to care does not appear to explain (summarize baed on RQ3). However, it is important that further exploration between diabetes, inflammation, and diabetes treatments take place. 

## Limitations

Among the different treatment options for diabetes, medication can mean either pills or insulin. There are different implications for these representative treatment options for inflammation and diabetes. However, we were not able to look at pills and insulin separately, or medication combinations, and some of their effects have the potential to cancel each other out.Given that we do not know exactly which medication people were taking, combination therapy is a possibility we could not account for. In addition, the sex variable was established through interviewer discernment and was not self reported. 

Because data analyzed are from cross-sectional studies only, we cannot infer causality and there are likely many factors that account for significant differences in inflammation levels among older Mexicans. 

\newpage

# Appendix

Despite the documented limitations of the World Health Organization Health State Description scale [@asadaMedicalTechnologiesNonhuman2005], it is worth exploring in future studies whether or not this scale captures diabetes complications in such a way that we might be able to analyze connections between inflammation and diabetes complications cross-sectionally in the SAGE data. 

\newpage

# References

<div id="refs"></div>

```{r Citations, eval=FALSE, include=FALSE}
citation("tidyverse")
citation("rio")
citation("here")
citation("papaja")
citation("tidyr")
citation("stargazer")
```

\newpage

# Tables and Figures




